Missing the Point$\colon$ Non-Convergence in Iterative Imputation Procedures

### 2020-04-24 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Add plot with rhat and ac to show pathological non-conv

**Dear Daniela, I have just implemented some major changes in my Methods and Results sections. Therefore, these are kind of a mess. Please do not waste any time on spelling/wording there, I will continue improving it. On the other hand, if you have general advice, please tell me because I'm happy to move thngs around still! Figures in the Results are currently missing, but will help in understanding the paper. Sorry that you won't have that now! Also, things written in bold are reminders for myself or things that I am unsure off still. Thanks already! - Hanne**

@@

<!-- (**or** Everybody who works with person data is likely to run into a missing data problem.) -->
Missing data problems are ubiquitous and pervasive in the social and behavioral sciences. If a dataset contains just one missing value for a variable of interest, statistical inferences are undefined and will not produce any result. Incomplete observations are therefore ignored by default in many statistical packages (i.e., list-wise deletion is employed). Unfortunately, this *ad hoc* solution may yield wildly invalid results [@buur18]. An alternative is to 'impute' (i.e., fill in) every missing value in an incomplete dataset. With imputation techniques, one or several completed datasets are created, on which statistical inferences can be performed. The case with several completed datasets is known as 'multiple imputation' [MI; @rubin76], and requires an additional step to pool the results across imputations **see figure 1??**.

**Move this after notation??** Figure \ref{fig:diagram} provides an overview of the steps involved with MI---from incomplete data, to $M$ completed datasets, to $M$ estimated quantities of interest ($\hat{Q}$s), to a single pooled estimate $\bar{Q}$. Missing data in $y$ is 'imputed' (i.e., filled in) $M$ times. The imputed data ($y_{imp}$) is combined with the observed data ($y_{obs}$) to create $M$ completed datasets. On each completed dataset, the analysis of scientific interest (the 'substantive model', or 'complete data model') is performed. The quantity of scientific interest (e.g., a regression coefficient) is denoted with $Q$. Since $Q$ is estimated on each completed dataset, $M$ separate $\hat{Q}$-values are obtained. These $M$ values are combined into a single pooled estimate $\bar{Q}$. **ALSO: make clear that iteration happens within the first step.**

>>>>

@@

<!-- (**or** Everybody who works with person data is likely to run into a missing data problem.) -->
Missing data problems are ubiquitous and pervasive in the social and behavioral sciences. If a dataset contains just one missing value for a variable of interest, statistical inferences are undefined and will not produce any result. To circumvent this, incomplete observations are ignored by default in many statistical packages (i.e., list-wise deletion is employed). Unfortunately, this *ad hoc* solution may yield wildly invalid results [@buur18]. An alternative is to 'impute' (i.e., fill in) every missing value in an incomplete dataset. With imputation techniques, one or several completed datasets are created, on which statistical inferences can be performed. The case with several completed datasets is known as 'multiple imputation' [MI; @rubin76], and requires an additional step to pool the results across imputations **see figure 1??**.

**Move this after notation??** Figure \ref{fig:diagram} provides an overview of the steps involved with MI---from incomplete data, to $M$ completed datasets, to $M$ estimated quantities of interest ($\hat{Q}$s), to a single pooled estimate $\bar{Q}$. Missing data in $y$ is 'imputed' (i.e., filled in) $M$ times. The imputed data ($y_{imp}$) is combined with the observed data ($y_{obs}$) to create $M$ completed datasets. On each completed dataset, the analysis of scientific interest (the 'substantive model', or 'complete data model') is performed. The quantity of scientific interest (e.g., a regression coefficient) is denoted with $Q$. Since $Q$ is estimated on each completed dataset, $M$ separate $\hat{Q}$-values are obtained. These $M$ values are combined into a single pooled estimate $\bar{Q}$. **ALSO: make clear that iteration happens within the first step, between incomplete and completed data.**
